Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-07 manuscript.tex
6 updates

When comparing the three different estimates for the RV, the SN mean RV presents standard errors that are 60\% larger than the N mean RV. However, the SN median RV gives errors 10\% more precise than N mean RV. 
The parameters describing the width of the CCF, FWHM and SN FWHM, have comparable standard errors. 
Finally, for the asymmetry parameters, $\gamma$ has standard errors that are 15\% more precise than BIS SPAN. 
In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV \jessi{I'm assuming you mean the median here?}, we are able to improve by 10\% the precision on the estimated RV, 15\% the precision on the estimated asymmetry, both without degrading the precision on the estimated width. 
SN mean RV should not be use to derive precise estimated RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived from N mean RV.
%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameters. When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved when fitting a Normal density (red triangles). However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. The use of the asymmetry SN parameter $\gamma$ leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN. Note that for the asymmetry, the error in BIS SPAN is in \ms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
   \label{fig:se}
\end{center}
\end{figure*}

>>>>

When comparing the three different estimates for the RV, the SN mean RV presents standard errors that are 60\% larger than the N mean RV. However, the SN median RV gives errors 10\% more precise than N mean RV. 
The parameters describing the width of the CCF, FWHM and SN FWHM, have comparable standard errors. 
Finally, for the asymmetry parameters, $\gamma$ has standard errors that are 15\% more precise than BIS SPAN. 
In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV \jessi{I'm assuming you mean the median here?}, we are able to improve by 10\% the precision on the estimated RV, 15\% the precision on the estimated asymmetry, both without degrading the precision on the estimated width. 
SN mean RV should not be use to derive precise estimated RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived from N mean RV.
%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
   \caption{\jessi{The stars used should be noted here}  Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM, and the asymmetry parameters. When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved when fitting a Normal density (red triangles). However, the standard errors for SN median RV (cyan crosses) are on average $10\%$ smaller than the standard errors coming from the N mean RV. The use of the asymmetry SN parameter $\gamma$ leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN. Note that for the asymmetry, the error in BIS SPAN is in \ms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN. \jessi{it would be good to have a "(top)" and "(bottom)" noted here.}}
   \label{fig:se}
\end{center}
\end{figure*}
